### 2023-09-15 project_Luis_PhD/paper.tex
anteproyecto v1

\def\Student{Luis Enrique Cuevas  Picos}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Luminosity measurement using Pixel Cluster Counting in the CMS experiment}
\def\ResearchLine{F\'{i}sica de Part\'{i}culas}

@@

\section{EXPECTED RESULTS}

From this project two main publications are expected:
\begin{itemize}
\item For the Run 2 luminosity mesurement, studies of the selection of good detector modules, calibration, background estimation, and calculation of the integrated luminosity, including the systematic uncertainties will be completed.
The results of these studies will be published in a peer-reviewed scientific journal.
\item For the Run 3 luminosity measurement, no measurement of the luminosity precision has been performed at this moment.
Similar studies as for the Run 2 dataset will be performed completed and a preliminary result of the luminosity measurement will be published.
\item For the development of the HL-LHC upgrade system, the work  will be based on the previously published Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
It is expected that this work will be presented at conferences and used for the final design and construction of the system to be installed in the LS3 (2025-2027).  
\end{itemize}

Also, the student will become a part of an international experiment and is expected to present his results at national or international scientific conferences.

\section{CALENDAR OF ACTIVITIES}

\begin{itemize}

\item {\bf Semester 1 (2023-2)}:
  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
  \SubItem{ Review of the literature.}
  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}

\item {\bf Semester 2 (2024-1)}:
  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
  \SubItem{ Start work on the 2023 dataset luminosity measurement. }

\item {\bf Semester 3 (2024-2)}:
  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
  \SubItem{ Start work on the 2024 dataset luminosity measurement. }

\item {\bf Semester 4 (2025-1)}:
  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
  \SubItem{ Writing of the monograph.}

\item {\bf Semester 5 (2025-2)}:
  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}

\item {\bf Semester 6 (2026-1)}:
  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}

\item {\bf Semester 7 (2026-2)}:
  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
  \SubItem{ Writing of the Ph.D thesis.}

\item {\bf Semester 8 (2027-1)}: 
  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
  \SubItem{ Defense of the Ph.D thesis.}

\end{itemize}

\onehalfspacing
\bibliographystyle{unsrt}
\bibliography{paper}

>>>>

\def\Student{Luis Enrique Cuevas  Picos}
\def\Title{ANTEPROYECTO}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Institution{Universidad de Sonora}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{Luminosity measurement using Pixel Cluster Counting in the CMS experiment}
\def\ResearchLine{Experimental Particle Physics}

@@

\newpage
\section{EXPECTED RESULTS}

From this project two main publications are expected:
\begin{itemize}
\item For the Run 2 luminosity mesurement, studies of the selection of good detector modules, calibration, background estimation, and calculation of the integrated luminosity, including the systematic uncertainties will be completed.
The results of these studies will be published in a peer-reviewed scientific journal.
\item For the Run 3 luminosity measurement, no measurement of the luminosity precision has been performed at this moment.
Similar studies as for the Run 2 dataset will be performed completed and a preliminary result of the luminosity measurement will be published.
\item For the development of the HL-LHC upgrade system, the work  will be based on the previously published Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
It is expected that this work will be used for the final design and construction of the system to be installed in the LS3 (2025-2027).  
\end{itemize}

The student will become parto of an international collaboration and is expected to present his results at national or international scientific conferences.

\section{CALENDAR OF ACTIVITIES}
\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{./calendario.pdf}
  \caption{ Calendar of activities }
  \label{fig:calendario}
\end{figure}

%\begin{itemize}
%
%\item {\bf Semester 1 (2023-2)}:
%  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
%  \SubItem{ Review of the literature.}
%  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
%  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}
%
%\item {\bf Semester 2 (2024-1)}:
%  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
%  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
%  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
%  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
%  \SubItem{ Start work on the 2023 dataset luminosity measurement. }
%  
%\item {\bf Semester 3 (2024-2)}:
%  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
%  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
%  \SubItem{ Start work on the 2024 dataset luminosity measurement. }
%  
%\item {\bf Semester 4 (2025-1)}:
%  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
%  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
%  \SubItem{ Writing of the monograph.}
%
%\item {\bf Semester 5 (2025-2)}:
%  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
%  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
%  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}
%  
%\item {\bf Semester 6 (2026-1)}:
%  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
%
%\item {\bf Semester 7 (2026-2)}:
%  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
%  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
%  \SubItem{ Writing of the Ph.D thesis.}
%  
%\item {\bf Semester 8 (2027-1)}: 
%  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
%  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
%  \SubItem{ Defense of the Ph.D thesis.}
%  
%\end{itemize}

\newpage
\onehalfspacing
\bibliographystyle{unsrt}
\bibliography{paper}
